### 2012-09-12 inst/examples/debug_uniform.Rmd
Fixed normalization of uniform integrals

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`

@@

```{r }
int_f <- function(f, x, q, sigma_m, sigma_i, pars){
  g <- function(X) f(X[1], X[2], pars)
  lower <- c(max(x - sigma_m, 0), max(q - sigma_i, 0))
  upper <- c(x + sigma_m, q + sigma_i)
  out <- adaptIntegrate(g, lower, upper)
  out$integral
}

F <- function(x,q, m, n, pars){
  K <- pars[2]
  out <- ((q+n-max(0,q-n))*(x+m-max(0,x-m))*(6*x*K-6*q*K-6*n*K+6*m*K+6*max(0,x-m)*K-6*
    max(0,q-n)*K-2*x^2+3*q*x+3*n*x-4*m*x-2*max(0,x-m)*x+3*max(0,q-n)*x-2*q^2-4*n*q+3*m*q+3*
    max(0,x-m)*q-2*max(0,q-n)*q-2*n^2+3*m*n+3*max(0,x-m)*n-2*max(0,q-n)*n-2*m^2-2*max(0,x-m)*m+3*
    max(0,q-n)*m-2*max(0,x-m)^2+3*max(0,q-n)*max(0,x-m)-2*max(0,q-n)^2))/(6*K)
  max(out,0)
}
```

@@

```{r}
  z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), 
               id = "stock")

ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable), shape="+")
dat <- subset(policy, stock < 140)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```

>>>>

`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="debug/", verbose=TRUE or`

@@

@@

```{r eval=FALSE, include=FALSE}
  z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
#policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1], mc=opt$D[,1]), id = "stock")
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], uniform = uniform$D[,1]), id = "stock")

ggplot(policy) + geom_jitter(aes(stock, stock-x_grid[value], color=variable), shape="+")
dat <- subset(policy, stock < 140)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,150, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```
